Software Ticket Quality

### 2017-10-30 proposal/mprop.tex
Add paper on data quality

@@

>>>>

% \textbf{}\cite{}:
% \begin{itemize}
%   \item \textbf{What were the goals?}
%   \item \textbf{What was the method?}
%   \item \textbf{What did they learn?}
%   \item \textbf{Relevance to our work}:
% \end{itemize}

@@

\textbf{Knowing-Why about Data Processes and Data Quality}\cite{lee2003knowing}:
\begin{itemize}
  \item \textbf{What were the goals?}
    They tried to investigate whether knowing-why affects work performance and
    whether knowledge held by people in different roles affect the overall work
    performance. 
  \item \textbf{What was the method?}
    They had 6 companies that served as data collection points. In all of them,
    the research focused on the quality of their customer activity data, tuned
    for the specific domain the company was activating in. They held 2 sessions
    at each company: in the first session, the participants were presented with
    an overview of the research and a questionnaire, while during the second 
    session provided summary feedback on the questionnaire results and gave the
    participants the chance to provide comments and explanations.
  \item \textbf{What did they learn?}
    The major finding of the study was that there is vast complexity of knowledge
    at work in data production process. 
  \item \textbf{Relevance to our work}: an important research on how knowledge in
    different roles in a company can lead to decreased data quality overall. It
    will help us to analyse the software tickets we will mine better.
\end{itemize}
